Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Proposition some more

The following propositions hold for both non-induced and induced subgraph-except-$k$ isomorphisms.

\begin{proposition}
    If $p \mapsto t$ then $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

>>>>

\begin{proposition}
    For both non-induced and induced subgraph-except-$k$ isomorphisms, if $p \mapsto t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

\begin{proposition}
    More powerfully, if $p \mapsto t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
    \operatorname{nds}(t)$.
\end{proposition}

As well as reasoning about degrees, we can also reason about paths.

\begin{proposition}
    If $p \mapsto t$ and $q \mapsto u$ then $\operatorname{paths}(p, q, 2) \le
    \operatorname{paths}(t, u, 2) + k$.
\end{proposition}

This leads to the following:

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and edges
    between vertices $p$ and $q$ if there are at least $n$ simple paths of length exactly $\ell$
    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[-k] \rightarrowtail
    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[-k]
    \rightarrowtail T^{n - k, 2}$.
\end{proposition}
